\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting — large bold small-caps with rule underneath
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\pdfgentounicode=1

%-------- CUSTOM COMMANDS --------
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-1pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemList}{\begin{itemize}[leftmargin=0.3in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\renewcommand\labelitemi{\small$\bullet$}

%=================================
\begin{document}
%=================================

%-------- HEADER --------
\begin{center}
  \textbf{\Huge Yogesh Kumar Pandey} \\ \vspace{4pt}
  \small
  +91 9839682710 \quad$|$\quad
  \href{mailto:ypandey.work@gmail.com}{ypandey.work@gmail.com} \quad$|$\quad
  Gorakhpur, Uttar Pradesh \\ \vspace{2pt}
  \href{https://linkedin.com/in/yogeshkumarpandey}{linkedin.com/in/yogeshkumarpandey} \quad$|$\quad
  \href{https://github.com/yogeshpandey800}{github.com/yogeshpandey800} \quad$|$\quad
  \href{https://yogeshpandey800.github.io/portfolio/}{Portfolio}
\end{center}

%-------- SUMMARY --------
\section{Summary}
\small
Computer Science student with practical experience building full-stack web
applications using the MERN stack (MongoDB, Express.js, React.js, Node.js).
Skilled in REST APIs, real-time communication with Socket.IO, JWT-based
authentication, and Cloudinary integration. Passionate about exploring new
technologies and using technical and problem-solving skills to build
high-impact software applications.

%-------- TECHNICAL SKILLS --------
\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Languages:} Java, JavaScript, Python, SQL}
  \resumeItem{\textbf{Frontend:} HTML, CSS, React.js, Tailwind CSS, Bootstrap}
  \resumeItem{\textbf{Backend:} Node.js, Express.js}
  \resumeItem{\textbf{Database:} MongoDB, Mongoose, MySQL}
  \resumeItem{\textbf{Tools:} Git, GitHub, Postman, Cloudinary, Socket.IO}
  \resumeItem{\textbf{Concepts:} REST APIs, Authentication (JWT), OOP}
  \resumeItem{\textbf{Communication:} English, Hindi}
\resumeSubHeadingListEnd

%-------- TECHNICAL EXPERIENCE --------
\section{Technical Experience}
\resumeSubHeadingList

  \resumeSubheading
    {CampusBuy -- Campus Marketplace Platform}{Feb 2026 -- April 2026}
    {Personal Project}{MMMUT, Gorakhpur}
  \resumeItemList
    \resumeItem{Designed and implemented an end-to-end campus-specific marketplace using the MERN stack to facilitate secure peer-to-peer buying and selling.}
    \resumeItem{Built institution-based authentication with OTP verification to restrict access to non-verified users.}
    \resumeItem{Created real-time buyer/seller chat using Socket.IO for seamless, low-latency interactions.}
    \resumeItem{Developed scalable RESTful APIs with JWT-based authentication for secure client-server communication.}
    \resumeItem{Integrated Cloudinary for image uploads, storage, and optimization to reduce loading times.}
    \resumeItem{Implemented modular features: product listings, wishlist, user/listing reporting, and lost \& found functionality.}
    \resumeItem{Built an accessible, responsive UI with Tailwind CSS for consistent cross-device experience.}
    \resumeItem{Architected backend services with clean, reusable code patterns.}
  \resumeItemListEnd

  \resumeSubheading
    {Online Bidding App}{Sept 2025 -- Nov 2025}
    {Personal Project}{MMMUT, Gorakhpur}
  \resumeItemList
    \resumeItem{Built a real-time web auction application enabling users to place competitive bids on items and services.}
    \resumeItem{Designed a reactive frontend UI displaying live bid progression, item listings, and result outcomes.}
    \resumeItem{Implemented backend logic for bid validation, concurrency control, and highest-bid tracking to ensure data integrity.}
    \resumeItem{Developed and consumed REST APIs for efficient front-end/back-end communication.}
    \resumeItem{Designed user authentication and session management for secure bidding workflows.}
    \resumeItem{Optimized for responsive performance across all device sizes.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-------- EDUCATION --------
\section{Education}
\resumeSubHeadingList
  \resumeSubheading
    {Master of Computer Applications}{2024 -- 2026}
    {MMMUT, Gorakhpur}{Gorakhpur, UP}
  \resumeSubheading
    {Bachelor of Computer Applications}{2020 -- 2023}
    {Ewing Christian College, Prayagraj}{Prayagraj, UP}
  \resumeSubheading
    {Class XII}{2019 -- 2020}
    {Prayag Public School}{Prayagraj, UP}
  \resumeSubheading
    {Class X}{2017 -- 2018}
    {Prayag Public School}{Prayagraj, UP}
\resumeSubHeadingListEnd

%-------- CERTIFICATIONS --------
\section{Certifications}
\resumeSubHeadingList
  \resumeItem{\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}Docker Essentials: A Developer Introduction & \href{https://www.credly.com/badges/f9846d29-a795-4b68-a675-92a107b7297b/}{Link}\end{tabular*}}
  \resumeItem{\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}Cybersecurity Fundamentals & \href{https://www.credly.com/badges/5fab2aae-370e-4394-8943-968a6b543add/}{Link}\end{tabular*}}
  \resumeItem{\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}Certificate of Internship -- CDAC & \href{https://drive.google.com/file/d/1ZfWZCH-HwEQ-o-4QeJT0aX5yP4xpy6jz/view?usp=sharing}{Link}\end{tabular*}}
\resumeSubHeadingListEnd

%-------- ACHIEVEMENTS --------
\section{Achievements}
\resumeSubHeadingList
  \resumeItem{Earned 5-star rating on HackerRank in Java, demonstrating strong problem-solving skills.}
  \resumeItem{Solved over 100 data structures and algorithms problems on LeetCode using Java.}
\resumeSubHeadingListEnd

\end{document}
