\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{3pt}

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1}}

% For education: course bold on top, institute italic below, tightly paired
\newcommand{\resumeEduEntry}[4]{%
  \vspace{2pt}
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \small #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \small #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.1in, label={}, itemsep=0pt, parsep=0pt, topsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemList}{\begin{itemize}[leftmargin=0.25in, itemsep=0pt, parsep=0pt, topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{1pt}}

\renewcommand\labelitemi{\small$\bullet$}

\begin{document}

%-------- HEADER --------
\begin{center}
  \textbf{\Huge Shiv Bahadur} \\ \vspace{3pt}
  \small
  +91 8604062618 \quad$|$\quad
  \href{mailto:shivbahadur00077@gmail.com}{shivbahadur00077@gmail.com} \quad$|$\quad
  \href{https://github.com/ShivBahadur007}{github.com/ShivBahadur007} \\ \vspace{1pt}
  \href{https://www.linkedin.com/in/shivbahadur007/}{linkedin.com/in/shivbahadur007} \quad$|$\quad
  \href{https://shivbahadur.netlify.app/}{shivbahadur.netlify.app}
\end{center}

\vspace{-4pt}

%-------- EDUCATION --------
\section{Education}
\vspace{2pt}
\resumeEduEntry{Master of Computer Applications}{2024 -- 2026}{MMMUT, Gorakhpur}{7.65 CGPA}
\resumeEduEntry{Bachelor of Computer Applications}{2021 -- 2024}{University of Allahabad, Prayagraj}{7.31 CGPA}
\resumeEduEntry{Class XII (CBSE)}{2021}{Jawahar Navodaya Vidyalaya, Mirzapur}{75\%}
\resumeEduEntry{Class X (CBSE)}{2019}{Jawahar Navodaya Vidyalaya, Mirzapur}{83.8\%}

%-------- INTERNSHIP / EXPERIENCE --------
\section{Internship / Experience}
\resumeSubHeadingList
  \resumeSubheading{Web Development Intern}{June 2025 -- July 2025}{CodeTech IT Solutions Pvt. Ltd.}{}
  \resumeItemList
    \resumeItem{Gained hands-on experience in front-end technologies including HTML, CSS, and JavaScript, along with modern frameworks like React.js to build interactive user interfaces.}
    \resumeItem{Participated in regular code reviews, improving code quality and learning industry-standard best practices for writing clean, maintainable code.}
    \resumeItem{Learned and applied version control workflows using Git \& GitHub, including branching, committing, and pull requests.}
    \resumeItem{\begin{tabular*}{0.93\textwidth}[t]{l@{\extracolsep{\fill}}r}Certificate & \href{https://drive.google.com/file/d/1KgT_eQ7jB2TjYmAnYwpTZK3kPhzV2Wyl/view?usp=drivesdk}{Link}\end{tabular*}}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-------- PROJECTS --------
\section{Projects}
\resumeSubHeadingList

  \resumeSubheading{Portfolio Website}{\href{https://github.com/ShivBahadur007/PortFolio--Shiv}{Project Link}}
    {Technologies Used: React.js, JavaScript, HTML, Tailwind CSS}{}
  \resumeItemList
    \resumeItem{Developed a personal portfolio website to showcase projects, skills, and certifications with a clean and professional layout.}
    \resumeItem{Implemented responsive design and smooth navigation using React.js, ensuring consistent experience across all screen sizes.}
    \resumeItem{Styled the entire application using Tailwind CSS utility classes for rapid and maintainable UI development.}
  \resumeItemListEnd

  \resumeSubheading{Online Learning Platform}{\href{https://github.com/ShivBahadur007/Online_learning_platform}{Project Link}}
    {Technologies Used: TypeScript, HTML, CSS}{}
  \resumeItemList
    \resumeItem{Built a fully responsive online learning platform using TypeScript, HTML, and CSS with a clean UI and structured educational content delivery.}
    \resumeItem{Leveraged TypeScript's static typing to improve code reliability and reduce runtime errors across the application.}
  \resumeItemListEnd

  \resumeSubheading{Tic Tac Toe Game}{\href{https://github.com/ShivBahadur007/tic-tac-toe}{Project Link}}
    {Technologies Used: JavaScript, HTML, CSS}{}
  \resumeItemList
    \resumeItem{Built a responsive browser-based Tic Tac Toe game using vanilla JavaScript, HTML, and CSS with complete game logic including win detection and draw conditions.}
    \resumeItem{Designed a clean and intuitive user interface ensuring smooth gameplay experience across different devices and screen sizes.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-------- SKILLS --------
\section{Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Technical:} HTML, CSS, JavaScript, Java, Python, C, C++, Express.js, React.js, Node.js, MongoDB}
  \resumeItem{\textbf{Soft Skills:} Management, Communication, Teamwork, Leadership and Mentoring}
  \resumeItem{\textbf{Tools:} VS Code, IntelliJ IDEA, Git, GitHub, Microsoft Office}
  \resumeItem{\textbf{Courses:} Data Structures and Algorithms, DBMS, Operating System, Computer Networks}
  \resumeItem{\textbf{Interests:} Artificial Intelligence, Machine Learning, Deep Learning, DevOps, Cybersecurity}
\resumeSubHeadingListEnd

%-------- CERTIFICATIONS --------
\section{Certifications}
\resumeSubHeadingList
  \resumeItem{\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}AI for Beginners -- HP LIFE Online Course & \href{https://www.life-global.org/certificate/fa11462e-24ff-4023-ba54-9b1e18671937}{Link}\end{tabular*}}
  \resumeItem{\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}Git \& GitHub Bootcamp -- Let's Upgrade & \href{https://drive.google.com/file/d/1CFZ9AnecDWjY0W88USr1vO-EbjyJivQS/view?usp=drivesdk}{Link}\end{tabular*}}
  \resumeItemList
    \resumeItem{Learned version control fundamentals, Git commands, and GitHub collaboration workflows including repositories, commits, branches, pull requests, and open-source contribution basics.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-------- ACHIEVEMENTS --------
\section{Achievements}
\resumeSubHeadingList
  \resumeItem{Solved more than 50 problems on various online coding platforms such as LeetCode, strengthening problem-solving and algorithmic thinking skills.}
  \resumeItem{Earned 5-star Badge in 30 Days of Code, Java, and Problem Solving challenges on HackerRank.}
  \resumeItem{Demonstrated proficiency in multiple programming languages including Java, JavaScript, SQL, and Python.}
\resumeSubHeadingListEnd

%-------- POSITION OF RESPONSIBILITY --------
\section{Position of Responsibility}
\resumeSubHeadingList
  \resumeSubheading{Event Coordinator -- Tech Fests}{April 2024}{University of Allahabad}{}
  \resumeItemList
    \resumeItem{Led a student team to plan, coordinate, and successfully organize a tech seminar for BCA students, managing logistics and scheduling.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-------- EXTRACURRICULAR --------
\section{Extracurricular}
\resumeSubHeadingList
  \resumeItem{Actively organized and managed society events like Technokratos, including spearheading the coding contest ByteBurst from planning to execution.}
  \resumeItem{Conducted live Python and Java programming classes for first-year students, helping them build a strong foundation in programming fundamentals.}
\resumeSubHeadingListEnd

\end{document}
